---
title: "Clinical and Epidemiological Aspects of Diphtheria: A Systematic Review and Pooled Analysis"
author: Shaun A. Truelove, Lindsay T. Keegan, William J. Moss, Lelia H. Chaisson, Emilie Macher,
  Andrew S. Azman, and Justin Lessler
date: "8/8/2018"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Clinical Course and Natural History

## Incubation period

```{r incubation_pd,eval=FALSE}
source('source/IncubPeriod_lognormal.R')
```

## Proportion asymptomatic

Calculation of proportion asymptomatic among never vaccinated ($p_0$)

```{r prop_asympt,eval=FALSE}
source('source/Prop_Symptomatic_Calculation.R')
```

Calculation of proportion asymptomatic among vaccinated ($p_{1,2}$, $p_3$)

```{r prop_asympt2,eval=FALSE}
source('source/Run_R0stan.R')
```

## Duration of colonization

Symptomatic cases and asymptomatic carriers

```{r colonization, eval=FALSE}
source('source/colonization_duration_shared.R')
```

Following receipt of penicillin or erythromycin, symptomatic cases

```{r clearance_antibiotics, eval=FALSE}
source('source/colonization_duration_treated.R')
```

## Case fatality ratio

For untreated, never vaccinated cases

```{r cfr_never_vaccinated,eval=FALSE}
source('source/cfr_nevervac_notreat.R')
```

By age

```{r cfr_age, eval=FALSE}
source('source/cfr_age.R')
```

By outbreak size

```{r cfr_outbreak_size, eval=FALSE}
source('source/cfr_outbreak_size.R')
```


# Epidemiology

## Proportion adult 

```{r proportion_adult, eval=FALSE}
source('source/age_distributions.R')
```

## Secondary cases caused by symptomatic and asymptomatic individuals

```{r tau, eval=FALSE}
source('source/Transmissibility.R')
source('source/Transmissibility.stan')

```

## CFR, Overall

```{r cfr_overall, eval=FALSE}
source('source/cfr_overall.R')
```

## CFR, by decade

```{r cfr_decade, eval=FALSE}
source('source/cfr_decade.R')
```

## Effective and Basic reproductive numbers

```{r Reproductive_numbers, eval=FALSE}
source('source/Run_R0Stan.R')
source('source/R0_and_Vc_fromStan.R')
```

## Serial interval/ Generation time

```{r generation_time, eval=FALSE}
source('source/GenerationTime_gamma.R')
```


# Treatment and Prevention

## CFR by diphtheria antitoxin treatment
```{r cfr_antitoxin, eval=FALSE}
source('source/cfr_antitoxin.R')
```

## CFR by antitoxin treatment delay
```{r cfr_antitoxin_delay, eval=FALSE}
source('source/cfr_antitoxin_delay.R')
```

## Clearance of diphtheria with antibiotics

```{r clearance_antibiotics2, eval=FALSE}
source('source/colonization_duration_treated.R')
```

## Vaccine Effectiveness

Overall

```{r VE_overall, eval=FALSE}
source('source/VE_by_dose.R')
```

Against severity/mortality

```{r VE_severity, eval=FALSE}
source('source/severity_by_vaccination.R')
```

Case fatality ratio, by vaccination status

```{r cfr_vacc, eval=FALSE}
source('source/CFR_vaccination.R')
```

Against colonization

```{r VE_colonization, eval=FALSE}
source('source/VE_against_colonization.R')
```

By age

```{r VE_age, eval=FALSE}
source('source/VE_by_age.R')
```

## Decline in proportion immune

By time since vaccination

```{r prop_immune_vacc, eval=FALSE}
source('source/immune_decline_time.R')
```

By age

```{r prop_immune_age, eval=FALSE}
source('source/immune_decline_age.R')
```


# Control and Outbreak Response

## Critical vaccination threshold

```{r vc, eval=FALSE}
source('source/Run_R0stan.R')
source('source/R0_and_Vc_fromStan.R')
```

```{r sensitivity_tau, eval=FALSE}
source('source/sensitivity_Vc_tau.R')
```

## Proportion of symptomatic individuals needed to isolate to halt the Rohingya outbreak at the beginning

```{r Rohingya_prop_isolate, eval=FALSE}
source('source/Prop_Sympt_Treat.R')
```
